Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-09-28 manuscript/manuscript.tex
Fixed typo
Fixed bad reference to Figure

We computed the three gravity fields  on every point of these four grids for different values of $D$, ranging from 0.5 to 10 with a step of 0.5.
Then we calculated the maximum difference between these results and the value of the analytical solution at the same height.

@@

The thickness of the sediment pack was obtained from \citet{Heine2007}.
We managed to produce a regular grid with a resolution of 0.05$^\circ$ on both longitude and latitude directions with one value of thickness on each node (see Figure \ref{fig:neuquen-basin}).

>>>>

We computed these gravity fields  on every point of the four grids for different values of $D$, ranging from 0.5 to 10 with a step of 0.5.
Then we calculated the maximum difference between these results and the value of the analytical solution at the same height.

@@

The thickness of the sediment pack was obtained from \citet{Heine2007}.
We managed to produce a regular grid with a resolution of 0.05$^\circ$ on both longitude and latitude directions with one value of thickness on each node (see Figure \ref{fig:neuquen-basin}b).
